non_phylo_analyses

### 2018-04-07 reports/non_phylo_model.Rmd
adding a weights vector to the model fitting. I think this is an important step and it seems to increase model fit (by just looking at the summary). But, happy to be told this is a crazy idea.

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-inner_join(response_variables,traits)
```

@@

naive_mod<-lm(log(urban_median)~log(mean_body_size)+log(clutch_size)+iucn_status+log(brain_size)+feeding_habitat_generalism+
     breeding_habitat_generalism+granivore+insectivore+carrion_eater+diet_generalism+
     movement_class+ground_nesting+hollow_nesting+nest_generalism+breeding+nest_aggregation+feeding_aggregation,data=df2,na.action = "na.fail")
summary(naive_mod)
dim(df2)
```

>>>>

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-left_join(traits,response_variables, by="binom") %>%
  filter(SCIENTIFIC_NAME_tree != "not_treated_as_species") %>%
  # drop columns that we aren't inerested in
  dplyr::select(-brain_size)
```

@@

naive_mod<-lm(log(urban_median)~log(mean_body_size)+log(clutch_size)+iucn_status+feeding_habitat_generalism+
     breeding_habitat_generalism+granivore+insectivore+carrion_eater+diet_generalism+plant_eater+
     movement_class+ground_nesting+hollow_nesting+nest_generalism+breeding+nest_aggregation+feeding_aggregation,data=df2,na.action = "na.fail", weights=(df2$N/df2$unique_localities))
summary(naive_mod)
dim(df2)
```
